Inequality in consumption

### 2017-02-28 inequality/consumption-inequality.Rmd
more plots for state-ineq

>>>>

These data break down, to some degree, by region: the fraction nonzero is highest for states in the South, but the inequality among users is highest for users in the Midwest.

```{r show_inequality_by_region}
regions = read_tsv('../../db/census-regions/census-regions.tsv') %>%
  select(state, region)

inequality_by_region = inequality_by_state %>%
  filter(consumption_metric=='n_claims') %>%
  left_join(regions, by='state')

inequality_by_region %>%
  ggplot(aes(x=n_bene, y=fraction_nonzero, color=region)) +
  geom_point() +
  xlab('number of beneficiaries in state') + ylab('fraction of beneficiaries with at least one claim') +
  theme_minimal()

inequality_by_region %>%
  ggplot(aes(x=n_bene, y=juran_nonzero, color=region)) +
  geom_point() +
  xlab('number of beneficiaries in state') + ylab('Juran index for days of antibiotics among users') +
  theme_minimal()
```
